---
title: "Portfolio_02"
author: "Enhui Wang"
date: "2025-02-01"
output: github_document
---

I worked on this project "Choose some data from EDA (Exploratory Data Analysis) or VDat (Visualizing Data); table or plot them in a way that Tukey/Cleveland didn’t." I created a combined density plot and heatmap visualization for the "sunday_weight" variable (i.e., represent weight data) for visualizing the shape of the distribution and the frequency of observations. 

```{r}
#open data
library(readr)
Data_01 <- read_csv("Data_01.csv")
View(Data_01)
library(ggplot2)
```
```{r}
#Filter out non NA in the sunday_weight variable 
filtered_data <- na.omit(Data_01$sunday_weight)

#create a data frame for plotting
plot_data <- data.frame(weight=filtered_data)

#ensure weight is numeric
plot_data$weight <- as.numeric(plot_data$weight)

```

```{r}
#create a density plot and heatmap for sunday_weight
plot <- ggplot(plot_data, aes(x = weight)) +
# the density curve is to visualize the overall shape of the distribution of the data
  geom_density(fill = "blue", alpha = 0.7) +
# the heatmap-like bins show how many data points fall within particular intervals; the visualization helps to see high or low-frequency regions.
  stat_bin(binwidth = 5, aes(y = ..count.., fill = ..count..),#add a binning layer and set each bin to cover 5 units in weight.
           geom = "tile", color = "white", alpha = 0.6) + #make the bins rectangular. 
  labs(
    title = "Density and Heatmap for Sunday Weight",
    x = "Sunday Weight (lbs)",
    y = "Density"
  ) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", name = "Frequency")
print (plot)

```
According to the plot, the peak is around 160 lbs. The darker blue bars suggest the highest frequencies occur around the peak of the density curve (e.g., 160 lbs), with progressively lower frequencies near the tails of the distribution.


